A simplified Plackett-Luce likelihood function for rank orders

### 2024-02-11 inst/ejs-sample.tex
rewording

Ranked data arises whenever multiple entities are sorted by some
criterion; the preferred interpretation is a race in which the
sufficient statistic is the order of competitors crossing the
finishing line.  The Plackett-Luce likelihood
function~\cite{luce1959,plackett1975} is a generalization of the
Bradley-Terry~\cite{bradley1952} in which non-negative strengths are
assigned to each competitor; without loss of generality, if the
finishing order is $1,2,\ldots,n$ and competitor $i$ has strength
$p_i\geqslant 0$, then the Plackett-Luce likelihood function will be
proportional to

\begin{equation}\label{plackettluce}
\prod_{i=1}^n\frac{p_i}{\sum_{j=i}^np_i}
\end{equation}

>>>>

Ranked data arises whenever multiple entities are sorted by some
criterion; the preferred interpretation is a race in which the
sufficient statistic is the order of competitors crossing the
finishing line.  The Plackett-Luce likelihood
function~\cite{luce1959,plackett1975} is a generalization of the
Bradley-Terry model~\cite{bradley1952} in which non-negative strengths
are assigned to each competitor; without loss of generality, if the
finishing order is $1,2,\ldots,n$ and competitor $i$ has strength
$p_i\geqslant 0$, then the Plackett-Luce likelihood function will be
proportional to

\begin{equation}\label{plackettluce}
\prod_{i=1}^n\frac{p_i}{\sum_{j=i}^np_j}
\end{equation}
